On the link between functional traits and growth rate: meta-analysis shows effects change with plant size, as predicted

### 2016-01-15 MS.tex
Change fig number in Table2 Fixed error in caption Fig3

\begin{figure}[h!]
\centering
\includegraphics[width=15cm,height=20cm,keepaspectratio]{output/Fig3.pdf}
\caption{The relationship between relative growth rates (RGR) and traits changes with plant stage and trait. Plots show the effect size (+ 95\% confidence intervals; CI) for the average correlation across >10 species, by plant stage. Effect size is a standardized measure of the deviation of correlation coefficient from zero (Fisher's z-transformed). Effects are significant if CIs for a given stage do not overlap with zero. Trait names as in Fig. \ref{fig:fig1}. $n$ indicates number of correlations contributing to each effect. Likelihood Ratio Tests (LRT) compared maximum-likelihood fits between a pooled model and one separated by stage. A significant p-value means adding a stage effect to the model significantly improved model fit. Results shown are from the ideal dataset (see methods for details).}
\label{fig:fig3}
\end{figure}

@@

\clearpage
\begin{table}[h!]
\centering
\caption{Check-list of criteria for meta-analysis in ecology developed by \citet{Koricheva:2014ku}.}
{\footnotesize
\vspace{0.5cm}
\begin{tabular}{p{0.2cm}p{4cm}p{0.8cm}p{7cm}}
  \hline
  & Quality criteria & Check & How and where is it addressed?\\
  \hline
  1.& Reporting full details of bibliographic searches & yes	& Complete details of bibliographic searches (i.e. electronic reference data bases that were searched, keywords, language, and search dates) are available in the ``Material and Methods''.\\
  2.& Reporting inclusion or exclusion criteria & yes & Inclusion criteria are specified in the ``Material and Methods''. A full list of all articles evaluated is available in the Appendix \ref{app:literature-snapshot}.\\
  3.& Weighting effect sizes by study precision & yes & Effects sizes were weighted by number of species. See	``Material and Methods'' for details.\\
 4.& Specifying meta-analytical model &	yes	& We use a mixed-effect model with a study ID as a random variable, and stage as a fixed effect. See ``Material and Methods'' for details. Results are shown in Fig. \ref{fig:fig3}.\\
 5.& Quantifying heterogeneity in effect sizes &	yes &	We estimate the extent of heterogeneity for each trait using the $I^{2}$ statistic. See Appendix \ref{app:supp_info_analyses} for details.\\
 6.& Exploring causes of heterogeneity & yes &	We explore the effect of stage, and the year of publication (see points 4 and 10 in this list).\\
 7.& Multifactorial analysis of explanatory variable	& yes & We check whether several other explanatory moderators (i.e. growth measurement, experiment type or growth form) are consistently the strongest predictors of the data. We do not test the multiple variables in a hierarchical fashion, because of the limited size of our dataset. See in Figs \ref{fig:figA4}f-j \& \ref{fig:figA6}.\\
  8.& Testing for publication bias &	yes	& We used several methods (i.e. funnel plots, the ``trim and fill'' method, and Rosenberg's fail-safe number). See Appendix \ref{app:supp_info_analyses} for details.\\
  9.& Sensitivity analysis &	yes &See ``Material and Methods'' for details, results in Figs \ref{fig:fig3} \& \ref{fig:figA5}.\\
  10.& Exploring temporal changes in effect size &	yes	& See Appendix \ref{app:supp_info_analyses} for details.\\
  11.& Controlling for phylogeny &	no &	It was not possible to control by the phylogeny, since the number of species used to measured each coefficient of correlation ranged from 2 to 300 species.\\
  12.& Specifying the software used &	yes	& See sections in ``Material and Methods'' and ``Availability of code and data''.\\
 13.& Providing reference list of primary studies included in the analysis &	yes &	All articles from which data were extracted are cited in the paper.\\
  14.& Providing the data set used for meta-analysis  &	yes &	A copy of the data set is available. See ``Availability of code and data'' for details.\\
   \hline
\end{tabular}
}
\label{tab:meta}
\end{table}

>>>>

\begin{figure}[h!]
\centering
\includegraphics[width=15cm,height=20cm,keepaspectratio]{output/Fig3.pdf}
\caption{The relationship between relative growth rates (RGR) and traits changes with plant stage and trait. Plots show the effect size (+ 95\% confidence intervals; CI) for the average correlation across $>$10 species, by plant stage. Effect size is a standardized measure of the deviation of correlation coefficient from zero (Fisher's z-transformed). Effects are significant if CIs for a given stage do not overlap with zero. Trait names as in Fig. \ref{fig:fig1}. $n$ indicates number of correlations contributing to each effect. Likelihood Ratio Tests (LRT) compared maximum-likelihood fits between a pooled model and one separated by stage. A significant p-value means adding a stage effect to the model significantly improved model fit. Results shown are from the ideal dataset (see methods for details).}
\label{fig:fig3}
\end{figure}

@@

\clearpage
\begin{table}[h!]
\centering
\caption{Check-list of criteria for meta-analysis in ecology developed by \citet{Koricheva:2014ku}.}
{\footnotesize
\vspace{0.5cm}
\begin{tabular}{p{0.2cm}p{4cm}p{0.8cm}p{7cm}}
  \hline
  & Quality criteria & Check & How and where is it addressed?\\
  \hline
  1.& Reporting full details of bibliographic searches & yes	& Complete details of bibliographic searches (i.e. electronic reference data bases that were searched, keywords, language, and search dates) are available in the ``Material and Methods''.\\
  2.& Reporting inclusion or exclusion criteria & yes & Inclusion criteria are specified in the ``Material and Methods''. A full list of all articles evaluated is available in the Appendix \ref{app:literature-snapshot}.\\
  3.& Weighting effect sizes by study precision & yes & Effects sizes were weighted by number of species. See	``Material and Methods'' for details.\\
 4.& Specifying meta-analytical model &	yes	& We use a mixed-effect model with a study ID as a random variable, and stage as a fixed effect. See ``Material and Methods'' for details. Results are shown in Fig. \ref{fig:fig3} \& \ref{fig:fig4}.\\
 5.& Quantifying heterogeneity in effect sizes &	yes &	We estimate the extent of heterogeneity for each trait using the $I^{2}$ statistic. See Appendix \ref{app:supp_info_analyses} for details.\\
 6.& Exploring causes of heterogeneity & yes &	We explore the effect of stage, and the year of publication (see points 4 and 10 in this list).\\
 7.& Multifactorial analysis of explanatory variable	& yes & We check whether several other explanatory moderators (i.e. growth measurement, experiment type or growth form) are consistently the strongest predictors of the data. We do not test the multiple variables in a hierarchical fashion, because of the limited size of our dataset. See in Figs \ref{fig:figA6}.\\
  8.& Testing for publication bias &	yes	& We used several methods (i.e. funnel plots, the ``trim and fill'' method, and Rosenberg's fail-safe number). See Appendix \ref{app:supp_info_analyses} for details.\\
  9.& Sensitivity analysis &	yes &See ``Material and Methods'' for details, results in Figs \ref{fig:fig4} \& \ref{fig:figA5}.\\
  10.& Exploring temporal changes in effect size &	yes	& See Appendix \ref{app:supp_info_analyses} for details.\\
  11.& Controlling for phylogeny &	no &	It was not possible to control by the phylogeny, since the number of species used to measured each coefficient of correlation ranged from 2 to 300 species.\\
  12.& Specifying the software used &	yes	& See sections in ``Material and Methods'' and ``Availability of code and data''.\\
 13.& Providing reference list of primary studies included in the analysis &	yes &	All articles from which data were extracted are cited in the paper.\\
  14.& Providing the data set used for meta-analysis  &	yes &	A copy of the data set is available. See ``Availability of code and data'' for details.\\
   \hline
\end{tabular}
}
\label{tab:meta}
\end{table}
